The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add Nmemb column, degrade sig figs in Table 1

\begin{deluxetable*}{cCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & 800\tablenotemark{f} & 685 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata

>>>>

\begin{deluxetable*}{cCCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{$N_{\text{memb}}$} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } & \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 740 & 174.9 & \sim20 & \sim -1700 & \sim0.005 & \sim11 & 352\tablenotemark{b} & 57 \\
Blanco1 & 489 & 237.2 & \sim2 & \sim-1800 & \sim2 & \sim210 & 410\tablenotemark{c} & 1460 \\
ComaBer & 153 & 85.9 & \sim2 & \sim-1900 & \sim0.7 & \sim140 & 112\tablenotemark{d} & 522\\
Hyades & 515 & 47.5 & \sim20 & \sim-1800 & \sim0.3 & \sim80 & 400\tablenotemark{e} & 462 \\
IC2391 & 325 & 151.6 & \sim6 & \sim-1800 & \sim0.02 & \sim20 & \nodata & \nodata \\
IC2602 & 492 & 152.2 & \sim10 & \sim-1700 & \sim0.3 & \sim89 & \nodata & \nodata \\
NGC2451A\tablenotemark{a} & 400 & 193.7 & \sim6 & \sim-1800 & \sim0.2 & \sim73 & \nodata & \nodata \\
Pleiades & 1326 & 135.8 & \sim20 & \sim-1700 & \sim0.4 & \sim96 & 800\tablenotemark{f} & 685 \\
Praesepe & 938 & 186.2 & \sim20 & \sim-1800 & \sim0.6 & \sim120 & 550\tablenotemark{d} & 781
\enddata
